Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/40-ocr-bench.tex
Small corrections everywhere

This section focuses on the evaluation of the performance of the three open-source OCR systems we selected, as described in \cref{sec:pipeline-summary}: Tesseract v4, Kraken and \peroocr.
The dataset used to perform this evaluation is composed of the $8,765$ entries (containing $424,764$ characters) from the dataset we previously introduced.
The single-column, cropped image of entries are used as input of each OCR system after a simple background whitening.
As pages were previously deskewed, text is mostly horizontal except for a few cases.
The expected output is the human transcription of these images provided in the dataset.
Before computing the Character Error Rate (CER) for each entry, each text prediction is normalized with the same basic rules as the ones used to post-process human transcriptions: dashes, quotes, and character code for some glyphs like stars or hands are normalized.
% Regarding the charset of each OCR, Tesseract predicts characters covering a large portion of Latin script, \peroocr generates characters with a similar range, sometimes predicting some Cyrillic characters, and Kraken is constrained by its English model to predict only ASCII characters.

@@

\includegraphics[width=\linewidth]{images/ocr-eval-2.pdf}
\medskip
}
\subcaptionbox{}[.5\linewidth]{
\includegraphics[width=\linewidth]{images/ocr-eval-1.pdf}
}
\caption{CER at entry-level for \peroocr, Kraken and Tesseract. (a) Global CER and distribution of the CER per entry. (b)
joint plot of the per-entry error rate showing that \peroocr and Tesseract do not fail on the same entries.}  
\label{fig.ocr-results}
\end{figure}
%
\Cref{fig.ocr-results} compares the performance of the OCR systems on our dataset. We can see Kraken's performance are
not as good as the two first OCR. This is partially due to the fact that the closest available model is for English text
and so it misses French specific symbols. On the over hand, even when using a French model trained on French 19th
documents, performance does not increase (and relaxing the character matching rules does not help either). Tesseract and
\peroocr are performing better on this dataset ``out-of-the-box''. With no fine-tuning, \peroocr gets the best accuracy
with less than 4\% character errors. Many of them are even due to a bad line detection in case of multi-lines entries
and are not related to the OCR system itself. \Cref{fig.ocr-results} (b) shows that errors from the two best OCR are not
committed on the same entries (if so, all points would be on the diagonal line) and that combining the outputs of
\peroocr and Tesseract could possibly improve the overall recognition quality. 
Also, we will not consider Kraken in the following NER experiments because its recognition rate is already too low.

>>>>

This section focuses on the evaluation of the performance of the three open-source OCR systems we selected, as described in \cref{sec:pipeline-summary}: Tesseract v4, Kraken and \peroocr.
The dataset used to perform this evaluation is composed of the $8,765$ entries (containing $424,764$ characters) from the dataset we previously introduced.
The single-column, cropped images of entries are used as input of each OCR system after a simple background whitening.
As the pages were previously deskewed, the text is mostly horizontal except for a few cases.
The expected output is the human transcription of these images provided in the dataset.
Before computing the Character Error Rate (CER) for each entry, each text prediction is normalized with the same basic rules as the ones used to post-process human transcription: dashes, quotes, and character codes for some glyphs like stars or hands are normalized.
% Regarding the charset of each OCR, Tesseract predicts characters covering a large portion of Latin script, \peroocr generates characters with a similar range, sometimes predicting some Cyrillic characters, and Kraken is constrained by its English model to predict only ASCII characters.

@@

\includegraphics[width=\linewidth]{images/ocr-eval-2.pdf}
\medskip
}
\subcaptionbox{}[.5\linewidth]{
\includegraphics[width=\linewidth]{images/ocr-eval-1.pdf}
}
\caption{CER at entry-level for \peroocr, Kraken and Tesseract. (a) Global CER and distribution of the CER per entry. (b)
joint plot of the per-entry error rate showing that \peroocr and Tesseract do not fail on the same entries.}  
\label{fig.ocr-results}
\end{figure}
%
\Cref{fig.ocr-results} compares the performance of the OCR systems on our dataset. We can see Kraken's performance are
not as good as the two first OCR. This is partially due to the fact that the closest available model is for English text
and so it misses French specific symbols. On the other hand, even when using a French model trained on French 19th
documents, the performance does not increase (and relaxing the character matching rules does not help either). Tesseract and
\peroocr are performing better on this dataset ``out-of-the-box''. With no fine-tuning, \peroocr gets the best accuracy
with less than 4\% character errors. Many of them are even due to a bad line detection in case of multi-lines entries
and are not related to the OCR system itself. \Cref{fig.ocr-results} (b) shows that errors from the two best OCR are not
committed to the same entries (if so, all points would be on the diagonal line) and that combining the outputs of
\peroocr and Tesseract could improve the overall recognition quality. 
In addition, we will not consider Kraken in the following NER experiments because its recognition rate is already too low.

### 2022-01-20 src-latex/parts/50-ner-xp1-training-set-size-and-pretraining.tex
Small corrections everywhere

\subsection{Training and evaluation protocol}
\label{sec:ner-xp1-protocol}
The following models form our baseline for both NER experiments.
Their short names written in square brackets will be used to reference them from now on.
\begin{itemize}
    \item \textbf{SpaCy NER pipeline for French~[SpaCy NER]}: We use the pipeline \textit{fr\_core\_news\_lg} provided by SpaCy v.3.2.1\mcite{spacy}, already trained for NER on the french corpora deep-sequoia and wikiner-fr.
    We stress again that we use the CNN version of this pipeline, not the transformer-based available in SpaCy v3.
    \item \textbf{Huggingface CamemBERT~[CmBERT]}: We rely on the implementation of BERT models provided by the software library Huggingface (transformers v.4.15.0, datasets v.1.17.0).
We chose to reuse a CamemBERT model published on the Huggingface repository \footnote{\url{https://huggingface.co/Jean-Baptiste/camembert-ner}} and already trained for NER on wikiner-fr.
\item \textbf{CamemBERT pretrained on Paris directories~[CmBERT+ptrn]}: 
To evaluate whether adapting CamemBERT to the domain increases its performance, we do an unsupervised pre-training of CmBERT for next sentence prediction and masked language modeling, using \num{845000} entries randomly sampled and OCRed with PERO.
The model is trained for 3 epochs and is available online\footnote{\url{https://huggingface.co/HueyNemud/das22-10-camembert_pretrained}}.
\end{itemize}

@@

\subsection{Results and discussion}
Figure \ref{fig:f1-vs-trainsize} displays the averaged precision, recall and F1-score for all models on the 8 subsets created from the groundtruth.
CmBERT, CmBERT+ptrn and SpaCy NER display the same behaviour: performances increase dramatically with the number of training examples and rapidly reach an area of slower progress around 1000 examples.
The F1 score increases by 4.6 points between 49 and 796 examples for CmBERT (resp. 1.6 for CmBERT+ptrn and 5.1 for SpaCy NER) but only by 1 point between 796 and 6373 examples (resp. 0.6 and 1.4).
The models derived from CamemBERT always outperform the Spacy model.

It appears that pre-training the CamemBERT model on OCR texts seems worth it only when a the training set used to fine-tune the NER layer is small.
This effect might be due to the differences in nature between the training subsets, whose texts are manually corrected, and the noisy OCR texts used to pretrain CamemBERT.
Indeed, the learned embeddings from the pret-raining are specialised on noisy texts and therefore less adapted to clean texts.
The pre-training aims at adapting the model to the vocabulary of the domain and to the errors caused by the OCR, which reveals not helpful and even counter-productive when the texts do not contain these types of errors.

>>>>

\subsection{Training and evaluation protocol}
\label{sec:ner-xp1-protocol}
The following models form our baseline for both NER experiments.
Their short names written in square brackets will be used to reference them from now on.
\begin{itemize}
    \item \textbf{SpaCy NER pipeline for French~[SpaCy NER]}: We use the pipeline \textit{fr\_core\_news\_lg} provided by SpaCy v.3.2.1\mcite{spacy}, already trained for NER on the French corpora deep-sequoia and wikiner-fr.
    We stress again that we use the CNN version of this pipeline, not the transformer-based available in SpaCy v3.
    \item \textbf{Huggingface CamemBERT~[CmBERT]}: We rely on the implementation of BERT models provided by the software library Huggingface (transformers v.4.15.0, datasets v.1.17.0).
We chose to reuse a CamemBERT model published on the Huggingface repository \footnote{\url{https://huggingface.co/Jean-Baptiste/camembert-ner}} and already trained for NER on wikiner-fr.
\item \textbf{CamemBERT pretrained on Paris directories~[CmBERT+ptrn]}: 
To evaluate whether adapting CamemBERT to the domain increases its performance, we do an unsupervised pre-training of CmBERT for next sentence prediction and masked language modeling, using \num{845000} entries randomly sampled and OCRed with PERO.
The model is trained for 3 epochs and is available online\footnote{\url{https://huggingface.co/HueyNemud/das22-10-camembert_pretrained}}.
\end{itemize}

@@

\subsection{Results and discussion}
Figure \ref{fig:f1-vs-trainsize} displays the averaged precision, recall, and F1-score for all models on the 8 subsets created from the groundtruth.
CmBERT, CmBERT+ptrn and SpaCy NER display the same behaviour: the performances increase dramatically with the number of training examples and rapidly reach an area of slower progress around 1000 examples.
The F1 score increases by 4.6 points between 49 and 796 examples for CmBERT (resp. 1.6 for CmBERT+ptrn and 5.1 for SpaCy NER) but only by 1 point between 796 and 6373 examples (resp. 0.6 and 1.4).
The models derived from CamemBERT always outperform the SpaCy model.

It appears that pre-training the CamemBERT model on OCR text seems worth it only when a the training set used to fine-tune the NER layer is small.
This effect might be due to the differences in nature between the training subsets, whose texts are manually corrected, and the noisy OCR texts used to pretrain CamemBERT.
Indeed, the learned embeddings from pre-training are specialised to noisy texts and therefore less adapted to clean text.
The pre-training aims at adapting the model to the vocabulary of the domain and to the errors caused by the OCR, which reveals not helpful and even counterproductive when the texts do not contain these types of errors.

### 2022-01-20 src-latex/parts/80-conclusion.tex
Small corrections everywhere

% !TeX root = ../main-paper.tex
\section{Conclusion}
We assessed the performances of three modern OCR systems on a set of historical sources of great interest in social history.
Although PERO-OCR clearly outperforms its competitors, the qualitative analysis of OCR errors shows that the failure cases are not the same for PERO and Tesseract.
This calls for leveraging both OCR systems in a complementary way to get the best of the two worlds.
%Moreover, we evaluate two deep-learning-based NER approaches in terms of their sensibility to the amount of training data and to noisy OCR texts.
The evaluation of SpaCy NER and CamemBERT (with and without pre-training) showed that BERT-based NER can benefit from pre-training and fine-tuning on a corpus produced with the same process than the texts to annotate.
%However, the results are not as good as for clean text: it is therefore interesting to investigate how to improve the OCR results or to correct the text in a postprocessing step.
Furthermore, it seems that all three models achieve good performance with relatively few training examples.
With a F1-score of 92\% with only 49 training examples, the pre-trained CamemBERT model seems to be a good choice to serve as a bootstrapping model in order to quickly produce large training sets and therefore lower the burden of creating a ground truth from scratch.
Besides, as directory entries always have the same structure - at least within a given index - we could take advantage of NER results and some simple rules to identify entries within pages instead of relying on the page layout.
%Interesting points to discuss:
%\begin{itemize}
%    \item can we train on noisy data? (without manual OCR correction?) => future work? cf Pero OCR training procedure?
%    \item do we need better OCR systems or better post-correction techniques (if NER is reliable enough)?
%    \item Construction of the lexicon and associated cost \nathalie{là je ne comprends pas}
%\end{itemize}
%Ideas for future work:
%\begin{itemize}
%    \item Evaluate this: fine-tune Spacy NER on a few samples to generated a bootstrap dataset, feed it to BERT (cleaned or raw) to create an good model with minimal efforts ? \nathalie{les résultats de la table 2 ne plaident pas vraiment pour ça: même sur les très petits corpus, spacy est tours derrière...}
%    \item Use ML to infer regexes ?
%    \item As directories entries are always structured the same way (in a given list at least): use NER to identify entries within pages to save the burden of having to rely on the page layout ?
%\end{itemize}

>>>>

% !TeX root = ../main-paper.tex
\section{Conclusion and future works}
We assessed the performance of three modern OCR systems on a set of historical sources of great interest in social history.
Although PERO-OCR clearly outperforms its competitors, the qualitative analysis of OCR errors shows that the failure cases are not the same for PERO and Tesseract.
This calls for leveraging both OCR systems in a complementary way to get the best of the two worlds.
%Moreover, we evaluate two deep-learning-based NER approaches in terms of their sensibility to the amount of training data and to noisy OCR texts.
The evaluation of SpaCy NER and CamemBERT (with and without pre-training) showed that BERT-based NER can benefit from pre-training and fine-tuning on a corpus produced with the same process than the texts to annotate.
%However, the results are not as good as for clean text: it is therefore interesting to investigate how to improve the OCR results or to correct the text in a postprocessing step.
Furthermore, it seems that all three models achieve good performance with relatively few training examples.
With a F1-score of 92\% with only 49 training examples, the pre-trained CamemBERT model seems to be a good choice to serve as a bootstrapping model to quickly produce large training sets and therefore lower the burden of creating a ground truth from scratch.
Besides, as directory entries always have the same structure - at least within a given index - we could take advantage of NER results and some simple rules to identify entries within pages instead of relying on the page layout.
%Interesting points to discuss:
%\begin{itemize}
%    \item can we train on noisy data? (without manual OCR correction?) => future work? cf Pero OCR training procedure?
%    \item do we need better OCR systems or better post-correction techniques (if NER is reliable enough)?
%    \item Construction of the lexicon and associated cost \nathalie{là je ne comprends pas}
%\end{itemize}
%Ideas for future work:
%\begin{itemize}
%    \item Evaluate this: fine-tune Spacy NER on a few samples to generated a bootstrap dataset, feed it to BERT (cleaned or raw) to create an good model with minimal efforts ? \nathalie{les résultats de la table 2 ne plaident pas vraiment pour ça: même sur les très petits corpus, spacy est tours derrière...}
%    \item Use ML to infer regexes ?
%    \item As directories entries are always structured the same way (in a given list at least): use NER to identify entries within pages to save the burden of having to rely on the page layout ?
%\end{itemize}
